Modeling browser-based distributed evolutionary computation systems

### 2015-02-07 modeling-volunteer-computing-gecco.tex
Well, something done...2

@@

\bibliographystyle{abbrv}
\bibliography{geneura,volunteer}

>>>>

The rest of the paper is organized as follows: next we will present
the state of the art in volunteer computing and its modelization. We
will proceed to describe the experimental setup in Section
\ref{sec:exp}, some preliminary results in Section \ref{sec:res} and
finally we will present our conclusions in Section \ref{sec:conc}
along with future lines of work.

\section{State of the art}
\label{sec:soa}

Using the web as a resource for distributed, or plainly user based,
evolutionary computation has a long history since JavaScript was
introduced as a browser-based language in 1997 and even before, when
other procedures, including Flash animations, VBScript, ActiveX or Java applets were
used. Java was pointed out in \cite{soares1998get} as a ``language for
internet'' and
\begin{quote}
Java can bring some important advantages... solves architectural
heterogeneity [...] easy to install and [...] built-in security
mechanisms
\end{quote}
The same paper by Soares et al. describes JET, a system that supports
the execution of parallel applications over the Internet. In fact the
same paper describes some other systems working at the same time,
except they cannot be used for science since they do not have a
comprehensive statistics support like JET.

However, Java (and all the other technologies) is not universal in the
sense than an extra component, namely, the Java virtual machine, has
to be installed in the browser. JavaScript
\cite{flanagan2006javascript} was introduced in 1997 as a
browser-embedded language and has, since them, become a set of standards
\cite{ECMA-262} for the language, its components and future versions
that have been widely adopted by the industry and also by scientists,
who used them for creating a non-distributed evolutionary algorithm on
the browser as early as 1998 \cite{jj-ppsn98}.

The potential for volunteer computing using browsers was realized
later on \cite{sarmenta-bayanihan} as well as the potential for
mischief of users with code in their hands
\cite{sarmenta-sabotagetolerance} however, these early efforts by
Sarmenta once again used Java and not JavaScript, making this effort
less universal. JavaScript can be used either for unwitting
\cite{unwitting-ec} or volunteer
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and has been used ever since by several
authors, including recent efforts \cite{duda2013distributed} that even
used the client's GPU \cite{duda2013gpu}.

There have been relatively few efforts to analyze what is the
performance that can be obtained from these volunteer computing
effort. There was some effort initially to dodge the issue by making
the algorithm adaptive to the kind of resources allotted to it
\cite{sarmenta-bayanihan}, which is actually not such a big problem in
algorithms such as the evolutionary algorithm that can easily be
paralelized via population splitting or farming out evaluations to all
the nodes available.

\section{Methodology}
\label{sec:exp}

@@

\bibliographystyle{abbrv}
\bibliography{geneura,volunteer,javascript,ror-js}
